Effect of Heteroscedasticity in Covariance Matrix

### 2014-11-04 thesis/draft4.tex
New scripts for verifying the theory of Mikosch.

  e^{-s^2/2v} q

@@

\frac{1}{x^2 + y^2} \label{eq:LognormalBlueImag}

@@

Now we consider equation \eqref{eq:LognormalBlueReal} and
\eqref{eq:LognormalBlueImag}. As $\lambda$ tends to $\lambda_\M$ with
$\lambda_\M \leq \infty$, $y \to 0$. Meanwhile, $x$ can neither tend
to 0 nor to $\infty$: If $x \to 0$, then $\frac{1}{x^2 + y^2} \to
\infty$ while the integral in \eqref{eq:LognormalBlueImag} tends to
$e^{8v}$ -- thus \eqref{eq:LognormalBlueImag} cannot hold. If instead
$x \to \infty$, RHS of \eqref{eq:LognormalBlueReal} tends to 0, failing
\eqref{eq:LognormalBlueReal}. So $x$ must tend to a finite value as $\lambda
\to \lambda_\M$. This limiting value, call it $a$, can be found from
\eqref{eq:LognormalBlueImag} by setting $y=0$:
\begin{eqnarray}
{1 \over a^2} &=& \int_{-\infty}^{\infty} \frac{ds}{\sqrt{2\pi v}}
\frac{
  e^{-s^2/2v} q
}{
  (e^{-2s} - qa)^2
} \label{eq:LognormalBlueImag2}
\end{eqnarray}
Clearly $a$ is a function of $v$ and $q$. Denote this function $f$
such that $a = f(v, q)$. As has been argued, $f(v,q)$ is finite for
all $v > 0$ and $0 < q \leq 1$. Using $f$, the integral in
\eqref{eq:LognormalBlueReal}, in the limit $\lambda \to \lambda_\M$,
can be expressed
\begin{eqnarray*}
  {1 \over \sqrt{2\pi v}} \int_{-\infty}^{\infty} \frac{
    e^{-2s - s^2/2v}
    }{
      (e^{-2s} - qa)^2
    } ds &=& {1 \over q e^{2v} f^2(v, qe^{-4v})}
\end{eqnarray*}
It immediately follows from \eqref{eq:LognormalBlueReal}
\begin{eqnarray*}
  \lambda_\M &=& {1 \over q e^{2v} f^2(v, qe^{-4v})}
\end{eqnarray*}
Since $q \leq 1$ and $e^{-2v} < 1$, $f(v, qe^{-2v})$ and hence
$\lambda_\M$ are finite. The spectrum is bounded.

The function $f(v,q)$ as defined by the largest root of
\eqref{eq:LognormalBlueImag2} is plotted in figure
\ref{fig:FFunction1}, seen as the intersection between the two curves,
which represent the two sides of \eqref{eq:LognormalBlueImag2},
respectively.
\begin{figure}[htb!]
  \centering
  \subfigure[]{
    \includegraphics[scale=0.35]{../pics/FFunctionOverview.eps}
    \label{fig:FFunctionOverview}
  }
  \subfigure[]{
    \includegraphics[scale=0.35]{../pics/FFunction1.eps}
    \label{fig:FFunction1}
  }
  %% \subfigure[$q = 0.5$]{
  %%   \includegraphics[scale=0.35]{../pics/FFunction3.eps}
  %%   \label{fig:FFunction2}
  %% }
  \caption{\small \it The implicit function $f(v, q)$ plotted in
    log-log scale. Blue: the integral $\int_{-\infty}^{\infty}
    \frac{ds}{\sqrt{2\pi v}}
    \frac{
      e^{-s^2/2v} q
    }{
      (e^{-2s} - qa)^2
    }$as a function of $a$. Green: the function $1/a^2$. v=0.1, q=0.1.
}
  \label{fig:FFunction}
\end{figure}

>>>>

  e^{-s^2/2v} q y

@@

\frac{y}{x^2 + y^2} \label{eq:LognormalBlueImag}

@@

Now we consider equation \eqref{eq:LognormalBlueReal} and
\eqref{eq:LognormalBlueImag}. When $q y$ and $v$ are both small, RHS
of \eqref{eq:LognormalBlueReal} and \eqref{eq:LognormalBlueImag} have
two sharp peaks, one at $s = 0$ and the other at $s = -{1 \over
  2}\ln(qx)$. We expand the integrands in
\eqref{eq:LognormalBlueReal} and \eqref{eq:LognormalBlueImag} around
these two peaks. For \eqref{eq:LognormalBlueImag} We write
\begin{eqnarray}
  {y \over x^2 + y^2} &=& \int_{-a}^{a} {e^{-s^2/2v}ds \over
    \sqrt{2\pi v}} \left[\frac{qy}{(1-qx)^2 + q^2y^2}\right] \label{eq:lambda}\\
  && - \int_{-b}^{b} {dt \over \sqrt{2\pi v}} {1 \over 2(t + q x)}
  \exp \left[-\frac{\log ^2(q x+t)}{8v}\right] {qy \over t^2 +
    q^2y^2} \nonumber \\
  &=& \erf\left({a \over \sqrt{2\pi}}\right)\left[\frac{qy}{(1-qx)^2 +
      q^2 y^2}\right] \nonumber \\
  && -{1 \over \sqrt{2\pi v}}\left\{
  \exp\left(-{\ln^2qx \over 8v}\right) \frac{x \cot ^{-1}\left(\frac{q
      y}{b}\right)+y \coth ^{-1}\left(\frac{q x}{b}\right)}{q x^2+q
    y^2} \right. \nonumber \\
  && \left.-\exp\left(-{\ln^2qx \over 8v}\right)
  \frac{y \left[x \log \left(1-\frac{2 b}{b+q x}\right)+2 y
    \cot^{-1}\left(\frac{q y}{b}\right)\right]}{2
    \left(x^2+y^2\right)} {\ln qx \over 4qvx}
  \right\} \nonumber
\end{eqnarray}
where $a$ and $b$ are small positive numbers. In particular, $b < q x$
such that $t + qx > 0$. Similarly, for \eqref{eq:LognormalBlueReal} we have
\begin{eqnarray}
  \lambda &=& {x \over x^2 + y^2} + \erf\left({a \over \sqrt{2v}}\right){1 - q x
    \over (1 - q x)^2 + q^2 y^2 } \nonumber \\
  && - {1 \over \sqrt{2\pi v}}
  \left\{\exp\left(-{\ln^2qx \over 8v}\right) \frac{x \log
    \left(1-\frac{2 b}{b+q x}\right)+2 y \cot ^{-1}\left(\frac{q
      y}{b}\right)}{2 q \left(x^2+y^2\right)} \right. \nonumber \\
  &&  
  \left. -\frac{\log (q x)}{4 q v x} \exp\left(-{\ln^2qx \over
    8v}\right) \frac{x \left[x \coth ^{-1}\left(\frac{q x}{b}\right)-y
    \cot ^{-1}\left(\frac{q y}{b}\right)\right]}{x^2+y^2}
  \right\} \label{eq:constraint}
\end{eqnarray}
%% Now we consider equation \eqref{eq:LognormalBlueReal} and
%% \eqref{eq:LognormalBlueImag}. As $\lambda$ tends to $\lambda_\M$ with
%% $\lambda_\M \leq \infty$, $y \to 0$. Meanwhile, $x$ can neither tend
%% to 0 nor to $\infty$: If $x \to 0$, then $\frac{1}{x^2 + y^2} \to
%% \infty$ while the integral in \eqref{eq:LognormalBlueImag} tends to
%% $e^{8v}$ -- thus \eqref{eq:LognormalBlueImag} cannot hold. If instead
%% $x \to \infty$, RHS of \eqref{eq:LognormalBlueReal} tends to 0, failing
%% \eqref{eq:LognormalBlueReal}. So $x$ must tend to a finite value as $\lambda
%% \to \lambda_\M$. This limiting value, call it $a$, can be found from
%% \eqref{eq:LognormalBlueImag} by setting $y=0$:
%% \begin{eqnarray}
%% {1 \over a^2} &=& \int_{-\infty}^{\infty} \frac{ds}{\sqrt{2\pi v}}
%% \frac{
%%   e^{-s^2/2v} q
%% }{
%%   (e^{-2s} - qa)^2
%% } \label{eq:LognormalBlueImag2}
%% \end{eqnarray}
%% Clearly $a$ is a function of $v$ and $q$. Denote this function $f$
%% such that $a = f(v, q)$. As has been argued, $f(v,q)$ is finite for
%% all $v > 0$ and $0 < q \leq 1$. Using $f$, the integral in
%% \eqref{eq:LognormalBlueReal}, in the limit $\lambda \to \lambda_\M$,
%% can be expressed
%% \begin{eqnarray*}
%%   {1 \over \sqrt{2\pi v}} \int_{-\infty}^{\infty} \frac{
%%     e^{-2s - s^2/2v}
%%     }{
%%       (e^{-2s} - qa)^2
%%     } ds &=& {1 \over q e^{2v} f^2(v, qe^{-4v})}
%% \end{eqnarray*}
%% It immediately follows from \eqref{eq:LognormalBlueReal}
%% \begin{eqnarray*}
%%   \lambda_\M &=& {1 \over q e^{2v} f^2(v, qe^{-4v})}
%% \end{eqnarray*}
%% Since $q \leq 1$ and $e^{-2v} < 1$, $f(v, qe^{-2v})$ and hence
%% $\lambda_\M$ are finite. The spectrum is bounded.

%% The function $f(v,q)$ as defined by the largest root of
%% \eqref{eq:LognormalBlueImag2} is plotted in figure
%% \ref{fig:FFunction1}, seen as the intersection between the two curves,
%% which represent the two sides of \eqref{eq:LognormalBlueImag2},
%% respectively.
%% \begin{figure}[htb!]
%%   \centering
%%   \subfigure[]{
%%     \includegraphics[scale=0.35]{../pics/FFunctionOverview.eps}
%%     \label{fig:FFunctionOverview}
%%   }
%%   \subfigure[]{
%%     \includegraphics[scale=0.35]{../pics/FFunction1.eps}
%%     \label{fig:FFunction1}
%%   }
%%   %% \subfigure[$q = 0.5$]{
%%   %%   \includegraphics[scale=0.35]{../pics/FFunction3.eps}
%%   %%   \label{fig:FFunction2}
%%   %% }
%%   \caption{\small \it The implicit function $f(v, q)$ plotted in
%%     log-log scale. Blue: the integral $\int_{-\infty}^{\infty}
%%     \frac{ds}{\sqrt{2\pi v}}
%%     \frac{
%%       e^{-s^2/2v} q
%%     }{
%%       (e^{-2s} - qa)^2
%%     }$as a function of $a$. Green: the function $1/a^2$. v=0.1, q=0.1.
%% }
%%   \label{fig:FFunction}
%% \end{figure}
